Proposal full title \\ Proposal Acronym

### 2001-10-09 drafts/IST/PartB.tex
toc update
svn path=/trunk/; revision=1507
small fix
svn path=/trunk/; revision=1508

\chapter*{B4. Contribution to program/Key action objectives}
\textit{This section, which should not exceed more than one page, describes how
the proposed Take-Up Action will contribute to the objectives of the program
and Key action. This can be done by describing how the proposal meets the
objectives and focus of the Action line which it addresses}
\\ \\

%% DRAFT, be nice GM
The NAME project completely follows the \" Take up Action\" second objective.
Indeed, it is designed to allow anybody even with limited ressources to install
a development for free software. Therefore, even smallest projects will have a
complete platform which will use the generic interfaces available on bigger
sites. Furthermore, free software related organizations will have a complete
packaged solution to provide all the needed tools for development. Since the
project is completely distributed, it will have little architecture
requirements and then will be easy to integrate into an existing network.
\\ \\
Furthermore, the availabiliy of such software that makes high quality 
free software development a reachable reality for everyone had already
encouraged free software development. Platforms like Savannah or SourceForge
have allowed a huge number of people to launch their project and to simplify
its diffusion. We are confident that the availability of an platform that is
trivial to install and configure will encourage the creation of lots of hosting
facilities in Europe and then encourages Free software development.
\chapter*{B5. Innovation}
\addcontentsline{toc}{chapter}{B5. Innovation}
\textit{This section, not exceeding two pages, describes the innovative
aspects of the proposed project. \\
Progress beyond the state of current practices within a user organization
should be described. The individual action steps must be described in the
context of the real business case. A separate description of this underlying
baseline project/target application - in terms of technical and business
parameters - must be included. Choice and justification for each of the new
practices including the supporting technologies (with comparison of not chosen
options) should be given (e.g. new methodologies, technologies, hardware and/or
software tools, subcontracted experts etc. -- whatever is applicable for the
experiment.}
\\ \\
%%% just cut & paste for now
\subsection*{Context}
Most of free or open source software is collaboratively developped using an
hosting plateform. The frontend integrates different functionnalities that are
available to project developpers and administrators and linked them with each
other. The backend is mainly implemented with scripts. \\

>>>>

\chapter*{B4. Contribution to program/Key action objectives}
\addcontentsline{toc}{chapter}{B4. Contribution to Key action objectives}
\textit{This section, which should not exceed more than one page, describes how
the proposed Take-Up Action will contribute to the objectives of the program
and Key action. This can be done by describing how the proposal meets the
objectives and focus of the Action line which it addresses}
\\ \\

%% DRAFT, be nice :-) . GM
The NAME project completely follows the \" Take up Action\" second objective.
Indeed, it is designed to allow anybody even with limited ressources to install
a development for free software. Therefore, even smallest projects will have a
complete platform which will use the generic interfaces available on bigger
sites. Furthermore, free software related organizations will have a complete
packaged solution to provide all the needed tools for development. Since the
project is completely distributed, it will have little architecture
requirements and then will be easy to integrate into an existing network.
\\ \\

Furthermore, the availabiliy of such software that makes high quality free
software development a reachable reality for everyone had already encouraged
free software development. Platforms like Savannah or SourceForge have allowed
a huge number of people to launch their project and to simplify its diffusion.
We are confident that the availability of a free and powerful platform in most
European language will encourage the creation of lots of hosting facilities in
Europe and then encourages Free software development.

\chapter*{B5. Innovation}
\addcontentsline{toc}{chapter}{B5. Innovation}
\textit{This section, not exceeding two pages, describes the innovative
aspects of the proposed project. \\
Progress beyond the state of current practices within a user organization
should be described. The individual action steps must be described in the
context of the real business case. A separate description of this underlying
baseline project/target application - in terms of technical and business
parameters - must be included. Choice and justification for each of the new
practices including the supporting technologies (with comparison of not chosen
options) should be given (e.g. new methodologies, technologies, hardware and/or
software tools, subcontracted experts etc. -- whatever is applicable for the
experiment.}
\\ \\
%%% just cut & paste for now
\subsection*{Context}
Most of free or open source software is collaboratively developped using an
hosting plateform. The frontend integrates different functionnalities that are
available to project developpers and administrators and linked them with each
other. The backend is mainly implemented with scripts. \\
